---
title: 'Join RStudio Cheat Sheets using the pdftools package'
author: Robert Kalcik
date: '2019-06-20'
bibliography: [../references/packages.bib]
link-citations: true
categories:
  - R
tags:
  - cheasheet
  - conference
header:
  caption: 'RStudio and various authors'
  focal_point: ''
---

```{r include = FALSE}
knitr::opts_chunk$set(eval = TRUE, collapse = TRUE, comment = NA, tidy = FALSE)
setwd(here::here("content/post/2019-06-20-join-rstudio-cheat-sheets-using-pdftools"))
library(fontawesome)
```

At the occastion of the [RISIS Summer School on Data Science in Science, Technology and Innovation Studies](https://www.risis2.eu/summer-schools/) I wanted to print all [RStudio cheatsheets](https://www.rstudio.com/resources/cheatsheets/). They are very well designed, speed up the coding and provide a good overview of the main functionality of a package. The regex, ggplot2, purrr and RMarkdown cheatsheets are my go to source. 

Garrett Grolemund at RStudio maintains the [github repo](https://github.com/rstudio/cheatsheets) of all contributed cheatsheets. Since the sheets have been contributed by members of the R Community under [CC-BY-4.0](https://creativecommons.org/licenses/by-sa/4.0/), I can share my merged files with you. You will find credits for each individual sheet author at the bottom of the page. 

Either download each cheatsheet into a folder or clone the github repo mentioned above (>900MB). Then, using the  [pdftools](https://ropensci.org/technotes/2019/04/24/pdftools-22/) package by [Jeroen Ooms](https://twitter.com/opencpu), I merged the one-sided and two-sided cheatsheets into to individual PDFs for easy printing :printer:

```{r cache = TRUE, warning = FALSE, eval = FALSE}
f <- list.files("cheatsheets/", pattern = "\\.pdf$", full.names = TRUE)
len <- purrr::map_int(f, pdftools::pdf_length)
pdftools::pdf_combine(f[len == 2], output = "2sided.pdf")
pdftools::pdf_combine(f[len == 1], output = "1sided.pdf")

```

You can download the output here:

* `r fa("download", fill = "#ee5863")` [2-sided cheatsheets](2sided.pdf)
* [1-sided cheatsheets](1sided.pdf) 

 




